On the number of tiles visited by a\\ line segment on a rectangular grid

### 2022-01-02 paper.tex
Revised abstract

\begin{abstract} % ***Alex: please check / revise 
The relationship between the length of a line segment and the number of tiles it visits on a rectangular grid is addressed in this paper. The square grid is also considered explicitly, as some of the specific problems studied are more tractable in that particular case. The segment position and orientation are modelled as either deterministic or random. In the former setting, the maximum number of visited tiles given the segment length and the infimum length for a desired number of visited tiles are characterized. For a segment of fixed length with random position and orientation, the average number of visited tiles and the probability of visiting the maximum number of tiles on a square grid are studied. These questions are related to Buffon's needle problem and its extension by Laplace.

>>>>

\begin{abstract}
Consider a line segment placed on a two-dimensional grid of rectangular tiles. This paper addresses the relationship between the length of the segment and the number of tiles it visits (i.e. has intersection with). The square grid is also considered explicitly, as some of the specific problems studied are more tractable in that particular case. The segment position and orientation can be modelled as either deterministic or random. In the deterministic setting, the maximum possible number of visited tiles is characterized for a given length, and conversely, the infimum segment length needed to visit a desired number of tiles is analyzed. The probabilistic setting regards the segment position and orientation as random. The average number of visited tiles and the probability of visiting the maximum number of tiles on a square grid are studied as a function of segment length. These questions are related to Buffon's needle problem and its extension by Laplace.
